% Copyright 2020 by Junwei Wang <i.junwei.wang@gmail.com>
%
% This file may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3c
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt

%\documentclass[compress]{beamer}
\documentclass[landscape,a4paper,]{beamer}

\newcommand\myheading[1]{%
  \par\bigskip
  {\Large\bfseries#1}\par\smallskip}

\newcommand\mysubheading[1]{%
  \par\bigskip
  {\Medium\bfseries#1}\par\smallskip}


\useoutertheme{infolines}
\graphicspath{{Images/}}

\usepackage[english]{babel}
\usepackage{metalogo}
\usepackage{listings}
\usepackage{fontspec}
\usepackage{tikz}

\usepackage{wrapfig}
\usetheme{Nord}
% \usetheme[style=light]{Nord}

\setmainfont{Yanone Kaffeesatz}
\setsansfont{Andika New Basic}
\setmonofont{DejaVu Sans Mono}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}

\author{Skshm}
\date{2021-10-19 Tue}
\title{1M1B Project Team 6}
\hypersetup{
 pdfauthor={Skshm},
 pdftitle={1M1B Project Team 6},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\newpage
\section{Immersive learning through Virtual Reality and Gamification}
\label{sec:org636766b}
Ideal Case Senario: Hook students up to a VR headset in class and attend it in the VR World.
Not a replacement of classes, rather a replacement of the classic chalk board and notebook teaching ??

\subsection{Positives}
\label{sec:orgd38d740}
\begin{itemize}
\item Bringing immersive learning to schools in an innovative way.
\item Letting children gasp abstract and practical concepts more easily.
\begin{itemize}
\item By Visuallizing said concepts in a VR Class.
\end{itemize}
\end{itemize}

\subsection{Negatives}
\label{sec:orgcfe40a0}

\section{Concepts}
\label{sec:org8b8dcf1}
\subsection{Subjects coverage}
\label{sec:orga4b5ffc}
Have a sandbox where they can build their own experiments and interact in their free time, share with eachother and learn.
Get Children excited about\ldots{} tech?
\subsubsection{Science}
\label{sec:org6de6cbc}
\begin{itemize}
\item Visualizing Atoms
\item Combustion Engines
\item Electric Diagrams
\item Biological life, evolution, aquatic life
\end{itemize}

\subsubsection{Social sciences}
\label{sec:orgc2e3ee9}
\begin{itemize}
\item Civilizations
\item Historical Events
\item Museums
\end{itemize}

\subsubsection{Abstract Concepts}
\label{sec:orgcd0d208}
\begin{itemize}
\item Mathamatical calculations
\begin{itemize}
\item Arithmetic
\item Volume and Suface Area
\end{itemize}
\item Music Theory (cant elaborate, I only play the guitar for fun)
\end{itemize}

\subsection{Building said Class}
\label{sec:orgea5c8bf}
\subsubsection{Hardware}
\label{sec:orge8e7469}
\begin{enumerate}
\item VR Headsets
\item Decision of handheld controllers or HoloLens style control
\end{enumerate}
\subsubsection{Software}
\label{sec:org1393ba9}
Would need to build a proof of concept in Unity (requires basic C\# and 'creative problem solving'?) - 5 hours to learn Unity + VR builds (ie 3D world building)
    Graphics in Blender (Requires 3D designing abilities) - 3 hours to learn minimum
    Could also just build a 2D concept sketch version if less time?

\begin{itemize}
\item 'Concept Shop' - Similar to something like the (Microsoft store)? for students categorized by Concepts
\begin{itemize}
\item Children can then create their own games using said concepts the way they do in \href{https:https://indreams.me/}{Indreams} (Looks comfortable for VR building elaborate to not say Indreams)
\end{itemize}
\end{itemize}
\end{document}